%% CloudKC-Bench — IEEE journal draft (IEEEtran).
%% Target: IEEE TIFS / Computers & Security. Compiles on Overleaf as-is.
%% Ownership (per plan v3 §11): Atishay = Abstract, System, Results, Failure Analysis,
%% Limitations. Anna = Introduction, Related Work, Discussion, Conclusion.
%% [RESULT] = fill from `benchmark.cli analyze/failures` once the run completes.
\documentclass[journal]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{array}
\usepackage{url}
\usepackage[hidelinks]{hyperref}

% Placeholders — make unfilled results impossible to miss.
\newcommand{\result}[1]{\textcolor{red}{\textbf{[RESULT: #1]}}}
\newcommand{\todo}[1]{\textcolor{blue}{[TODO: #1]}}
\newcommand{\cmark}{\ensuremath{\checkmark}}
\newcommand{\xmark}{\ensuremath{\times}}

\begin{document}

\title{CloudKC-Bench: An Open Benchmark and Controlled Study of LLM
Cross-Domain Correlation for AWS Multi-Stage Kill-Chain Reconstruction}

\author{Atishay~Jain,~Anna~M.,~and~S.~Nagasundari%
\thanks{The authors are with the Centre for Information Security, Forensics and
Cyber Resilience (ISFCR), PES University, Bengaluru, India.}%
\thanks{Corresponding author: Atishay Jain (e-mail: atishay.offical@gmail.com).}}

\markboth{Preprint --- draft \today}{Jain \MakeLowercase{\textit{et al.}}: CloudKC-Bench}

\maketitle

\begin{abstract}
Multi-stage attacks on cloud infrastructure leave traces scattered across
heterogeneous control-plane and network telemetry---IAM/CloudTrail API events, VPC
Flow Logs, S3 access logs, and EC2 lifecycle events---such that no single source
contains a whole attack. Whether Large Language Models (LLMs) can correlate across
these sources to reconstruct the kill chain, and whether they do so better than
simpler baselines, is an open and largely unmeasured question. We present
\emph{CloudKC-Bench}, the first open benchmark targeting AWS control-plane
multi-stage kill-chain reconstruction: a taxonomy-structured set of
$\sim$70 scenarios grounded in documented real incidents and ATT\&CK-for-Cloud
techniques, each released with a machine-checkable ground-truth manifest and a
published mechanical matching function. Using the benchmark we run a pre-registered
four-arm ablation (multi-agent LLM, single-agent LLM, single agent without a
pre-filter, and a deterministic rules-only correlator) plus an independent community
Sigma-rules baseline, holding model, telemetry, and compute fixed across arms.
We report standard detection metrics per scenario category with bootstrap confidence
intervals and effect sizes, and resolve two pre-registered hypotheses. In a preliminary
run (qwen2.5:7b, multi-stage category), the LLM performs cross-domain attack-\emph{event}
detection competitively and at higher precision than the rules ($\geq 0.94$ vs $0.73$),
but is markedly worse at exact ATT\&CK-\emph{technique} attribution; multi-agent
decomposition adds no measurable value over a single agent.
\todo{finalise abstract numbers after the full-category + real-telemetry runs.}
We further quantify the cost/latency of the deterministic pre-filter and give a
failure-mode taxonomy showing when and why reconstruction fails. All artifacts---the
generator, manifests, schema, matching function, and analysis scripts---are released
to enable independent replication.
\end{abstract}

\begin{IEEEkeywords}
Cloud security, threat detection, large language models, benchmark, MITRE ATT\&CK,
kill-chain reconstruction, AWS, multi-agent systems.
\end{IEEEkeywords}

% =====================================================================
\section{Introduction}\label{sec:intro}
% Owner: Anna
Cloud control-plane telemetry is siloed by design: a single attack stage such as
privilege escalation surfaces in CloudTrail, while the ensuing exfiltration surfaces
in S3 access logs \emph{and} VPC Flow Logs. Reconstructing a multi-stage kill chain
therefore requires correlation \emph{across} telemetry sources that share no join key
and arrive with different, variable delivery latencies. LLMs have been proposed for
security triage, but claims about their value are frequently made without fair
baselines, without reproducible data, and without honest treatment of
non-determinism---exactly the flaws that sink security-ML papers.

\textbf{Problem.} Given heterogeneous AWS control-plane and network telemetry produced
during a multi-stage attack, reconstruct the kill chain---identify which events belong
to the attack, in what order, mapped to which ATT\&CK-for-Cloud techniques---and do so
measurably better, or measurably no better, than fair baselines.

\textbf{Gap.} There is no public AWS control-plane multi-stage kill-chain dataset with
machine-checkable ground-truth manifests (Section~\ref{sec:related}). Existing cloud
security benchmarks target a different platform (Azure), a different task (malware
analysis, threat-intel reasoning, architectural threat modeling, insider threat), or
produce detection rules rather than reconstructed chains.

\textbf{Contributions.}
\begin{itemize}
\item \textbf{C1.} \emph{CloudKC-Bench}, the first open benchmark targeting AWS
control-plane multi-stage kill chains, with ground-truth manifests and a published
mechanical matching function (Section~\ref{sec:bench}).
\item \textbf{C2.} A pre-registered four-arm ablation on identical telemetry that
attributes any detection advantage to a specific layer---pre-filter, LLM, or
multi-agent decomposition (Sections~\ref{sec:setup},~\ref{sec:results}).
\item \textbf{C3.} A first-class cost/latency analysis of deterministic pre-filtering,
with measured per-category filtering ratios and a cost--accuracy trade-off.
\item \textbf{C4.} A failure-mode taxonomy: which categories, techniques, and
false-positive patterns break reconstruction (Section~\ref{sec:failure}).
\item \textbf{C5.} A reproducibility artifact: pinned model, frozen scenarios, released
code, manifests, and analysis scripts.
\end{itemize}
We deliberately state H2 as a null and report negative results honestly; the benchmark
stands as a contribution regardless of whether the system ``wins''.

% =====================================================================
\section{Background}\label{sec:background}
% Owner: Atishay
\subsection{AWS control-plane telemetry}
CloudSentinel/CloudKC-Bench considers four sources. \emph{CloudTrail} records every
API call (\texttt{eventName}, \texttt{userIdentity}, \texttt{sourceIPAddress},
\texttt{eventTime}, request/response elements); its S3 delivery latency is typically
5--15 minutes. \emph{VPC Flow Logs} record accepted/rejected IP traffic at the ENI
level (\texttt{srcaddr}, \texttt{dstaddr}, ports, protocol, action, bytes).
\emph{S3 access logs / data events} record object operations (\texttt{GetObject},
\texttt{PutObject}, \texttt{DeleteObject}, \texttt{CopyObject}). \emph{EC2 lifecycle}
events record launches, terminations, and image/snapshot operations.

\subsection{Kill chains and ATT\&CK for Cloud}
A multi-stage cloud attack follows a recognisable progression (initial access,
persistence, privilege escalation, defense evasion, credential access, discovery,
lateral movement, exfiltration, impact), each stage typically visible in a different
telemetry source. We ground every scenario stage in an ATT\&CK-for-Cloud technique
identifier so that realism is externally citable rather than asserted.

\subsection{LLMs for security triage}
Prior work applies LLMs to explanation, rule generation, and QA over security logs.
Our position is that the multi-agent architecture is an \emph{instrument}, not a
contribution: its value is tested by ablation, and a null result is a valid finding.

% =====================================================================
\section{Related Work}\label{sec:related}
% Owner: Anna. Coverage-gap assessment from docs/week1/09 (papers read, Jul 2026).
We organise prior work as a taxonomy and, for each theme, state what it leaves open.

\subsection{LLM-assisted security detection}
LLMCloudHunter~\cite{schwartz2025llmcloudhunter} generates Sigma detection-rule
candidates from cyber-threat-intelligence reports for cloud, and HuntGPT~\cite{ali2023huntgpt}
couples a random-forest network IDS on KDD99 with GPT-3.5 for explanation.
\emph{Leaves open:} both target rule generation or single-host anomaly explanation, not
reconstruction of multi-stage AWS control-plane kill chains with mechanical scoring.

\subsection{Cloud-native threat detection}
Managed services (e.g., GuardDuty) and attack-emulation tooling such as Stratus Red
Team~\cite{stratus} and CloudGoat~\cite{cloudgoat} define ATT\&CK-mapped AWS techniques.
\emph{Leaves open:} these are detectors or attack generators, not open benchmarks with
ground-truth manifests and a published matching function.

\subsection{Multi-agent architectures for security}
Agentic and provenance-based hunting~\cite{mukherjee2025provenance} report gains from
RAG and agent orchestration on host-provenance graphs.
\emph{Leaves open:} host endpoint forensics, not cloud control-plane correlation; the
value of decomposition is asserted, rarely ablated---our H2 tests it directly.

\subsection{Security benchmarks: design, coverage, and gaps}
Table~\ref{tab:coverage} positions CloudKC-Bench against the five closest benchmarks.
CyberSOCEval~\cite{deason2025cybersoceval} evaluates malware analysis and threat-intel
reasoning; ExCyTIn-Bench~\cite{wu2025excytin} builds an \emph{Azure} threat-investigation
benchmark scored as QA over investigation graphs; OrgForge-IT~\cite{orgforge2026} is a
verifiable synthetic \emph{insider-threat} benchmark; and ACSE-Eval~\cite{acseeval2025}
evaluates LLM threat \emph{modeling} of AWS architecture/IaC. No competitor satisfies all
six properties simultaneously.
\emph{Leaves open:} an AWS-control-plane, telemetry-driven, machine-checkable
kill-chain-reconstruction benchmark---the gap CloudKC-Bench fills.

\begin{table*}[t]
\caption{Coverage gap. \cmark~yes, \xmark~no, $\circ$~partial. Assessed from the
papers (Jul 2026); partial cells to be confirmed against full text.}
\label{tab:coverage}
\centering
\begin{tabular}{lcccccc}
\toprule
Property & CyberSOCEval & ExCyTIn & OrgForge-IT & LLMCloudHunter & ACSE-Eval & \textbf{Ours} \\
\midrule
AWS control-plane specific      & \xmark & \xmark & \xmark & $\circ$ & $\circ$ & \cmark \\
Multi-stage kill chains         & \xmark & \cmark & \xmark & \xmark  & \xmark  & \cmark \\
Open + reproducible             & \cmark & \cmark & \cmark & \xmark  & \cmark  & \cmark \\
Machine-checkable ground truth  & $\circ$ & \cmark & \cmark & \xmark & $\circ$ & \cmark \\
ATT\&CK-for-Cloud mapped        & \xmark & \xmark & \xmark & $\circ$ & $\circ$ & \cmark \\
Real-AWS validated              & \xmark & \xmark & \xmark & \xmark  & \xmark  & $\circ$ \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Kill-chain and ATT\&CK modeling}
MITRE ATT\&CK for Cloud~\cite{mitreattack} provides the technique taxonomy we use to
label stages. \emph{Leaves open:} a scored reconstruction task over live telemetry.

% =====================================================================
\section{CloudKC-Bench Design}\label{sec:bench}
% Owner: Atishay
\subsection{Scenario taxonomy}
The benchmark comprises $\sim$70 scenarios across five never-pooled categories:
single-domain attacks (12; a sanity floor), multi-stage kill chains (15; the primary
test), low-and-slow evasion (12), ephemeral compute (10), and benign noise (10;
false-positive measurement), plus a sealed held-out set (10). Every scenario cites a
documented real incident pattern (e.g., the Capital One 2019 SSRF$\rightarrow$IMDS
$\rightarrow$S3 chain~\cite{capitalone2019}, SCARLETEEL~\cite{scarleteel2023}, TeamTNT
cryptojacking~\cite{teamtnt2020}) and one or more ATT\&CK-for-Cloud techniques.

\subsection{Ground-truth manifests and the answer-key boundary}
Each scenario ships a machine-checkable manifest: an ordered list of stages, each with a
technique id, telemetry source, evidence event ids, and a timestamp range, validated
against a published JSON Schema. Crucially, ground truth lives \emph{only} in the
manifest and an \texttt{is\_ground\_truth} flag---never in the event payload the systems
read---so an attack API call is, in isolation, indistinguishable from benign activity.

\subsection{Mechanical matching function}
Scoring is an exact, deterministic function of (reconstructed chain, manifest); no human
or LLM judging. A reported stage matches a ground-truth stage iff the technique id and
telemetry source match \emph{and} the cited evidence overlaps the ground-truth evidence
(preventing ``right answer, wrong reason'' credit). Matching is one-to-one; partial credit
is awarded per stage; order is scored via a documented penalty. Benign scenarios have no
stages, so any reported stage is a false positive.

\subsection{Quality controls}
Real-incident grounding, inter-rater review of $\geq$20\% of scenarios, and an authorship
separation for the held-out set (sealed before system finalisation) address the
synthetic-realism and selection-bias threats. A measured cross-service clock model
documents delivery lag/skew so temporal claims are defensible.

% =====================================================================
\section{System Architecture}\label{sec:system}
% Owner: Atishay. The architecture is the instrument, not the contribution.
Telemetry is normalised into a SQLite state cache. A deterministic, instrumented
pre-filter reduces event volume before any LLM call, recording events-in/out and
pre-filter recall. The full system (arm A1) distributes filtered events to four domain
hunters (CloudTrail, VPC, S3, EC2), whose candidate detections a coordinator correlates
into an ordered chain. All arms emit the identical reconstructed-chain schema, so the
comparison is not confounded by output format. The LLM backend is pluggable---a
deterministic offline backend for reproducible pipeline tests, a local Ollama model, or a
hosted API (Gemini/OpenAI-compatible)---and is pinned per experiment.

% =====================================================================
\section{Experimental Setup}\label{sec:setup}
% Owner: Atishay
\subsection{Arms and baselines}
Four arms hold model, telemetry, and compute fixed and vary one factor each:
\textbf{A1} pre-filter + multi-agent; \textbf{A2} pre-filter + single agent
(A1 vs A2 isolates decomposition, H2); \textbf{A3} single agent on raw logs
(A2 vs A3 isolates the pre-filter, C3); \textbf{A4} pre-filter + deterministic rules,
no LLM (A1/A2 vs A4 isolates the LLM, H1). An independent community Sigma-rules
baseline (\textbf{SIGMA}) guards against the objection that A4 was designed to lose.

LLMCloudHunter~\cite{schwartz2025llmcloudhunter} generates detection \emph{rules} from
CTI reports rather than reconstructing kill chains from live telemetry; comparing it on
CloudKC-Bench would be a task mismatch, so it is positioned in the related-work taxonomy
(Section~\ref{sec:related}) rather than run as a benchmark arm. GuardDuty requires
real-AWS access with a $\geq$7-day warm-up period; it is deferred to a real-AWS
follow-up study (Section~\ref{sec:threats}); SIGMA already provides an independent
rules comparison that does not depend on a managed service.

\subsection{Environments}
Scenarios run in two environments emitting the identical schema: a reproducible layer
(deterministic synthetic generation / LocalStack), and---budget-gated---a real-AWS
sandbox for external validity. Real-AWS results, where available, are the headline;
the reproducible layer is the consistency check.

\subsection{Pre-registration and power}
The research question, H1's required margin ($\geq 0.15$ absolute multi-stage recall),
H2's equivalence band, and all tests were fixed in writing before any result. An a-priori
power analysis (paired design, $\alpha=0.05$, power $0.80$) shows that after
Holm--Bonferroni over the full comparison grid no category reaches the corrected $n$ for
moderate effects; we therefore pre-register \emph{two} primary confirmatory tests
(H1 and H2 on the multi-stage category) and treat all other comparisons as exploratory,
reported with effect sizes and bootstrap confidence intervals.
\todo{state the pinned model + date + seed list once Anna's run is fixed.}

\subsection{Metrics and protocol}
Primary metrics are TPR/recall, FPR, precision, F1, and AUC where meaningful, reported
\emph{per category}. The unit of analysis is the scenario; seeds are repeated measures
aggregated to the scenario level. Effect sizes (Cohen's $d_z$) and bootstrap 95\%
confidence intervals are primary; $p$-values (paired permutation test) are secondary and
Holm--Bonferroni corrected.

\textbf{TCP disjoint-stream robustness test (DoD item 11).}
The correlator assigns stage order by sorting candidates on \texttt{event\_time};
different telemetry sources carry source-specific delivery lags (CloudTrail $\sim$7 min,
VPC $\sim$75 s, EC2 $\sim$30 s). We sweep a per-source timestamp offset $\Delta T \in
[-900, +900]$ s and measure the minimum $|\Delta T|$ at which \texttt{order\_penalty}>0
(\emph{robustness threshold}). This threshold is reported alongside the clock-model skews
(Section~\ref{sec:background}) to justify the correlation window choice. Crucially,
recall is invariant to $\Delta T$ (the matching function does not use timestamps), so a
rising order penalty represents a pure ordering failure rather than a detection failure.
Run \texttt{python -m benchmark.cli tcp-robustness} to reproduce.

% =====================================================================
\section{Results}\label{sec:results}
% Owner: Atishay.
\noindent\textbf{Preliminary run.} The numbers below are a first, internally-valid result on the
\emph{multi-stage} category (15 scenarios, 3 seeds) with \textbf{qwen2.5:7b} (served locally via Ollama) as the
LLM and the \emph{synthetic} telemetry backend. Full-category and real-telemetry (LocalStack) runs are in
progress; the framing and pipeline are fixed, only the numbers will grow. \todo{extend to all categories +
real telemetry; add a second, larger model.}

\subsection{Two scoring lenses}
We report reconstruction under two lenses (Section~\ref{sec:bench}): \emph{technique-level} (a stage is
correct only if the ATT\&CK technique, telemetry source, and cited evidence all match) and \emph{event-level}
(technique-agnostic: did the arm cite the ground-truth attack \emph{events} at all?). Table~\ref{tab:twolens}
shows they tell very different stories.

\begin{table}[t]
\caption{Multi-stage kill chains: two scoring lenses (qwen2.5:7b, synthetic, $n{=}15$, 3 seeds).
Technique-level uses parent-technique credit; event-level is technique-agnostic.}
\label{tab:twolens}
\centering
\begin{tabular}{lcccc}
\toprule
 & A1 & A2 & A3 & \textbf{A4 (rules)} \\
\midrule
Technique-level recall      & 0.037 & 0.011 & 0.041 & \textbf{0.911} \\
Event-level recall          & 0.674 & 0.641 & 0.732 & 0.967 \\
Event-level precision       & 0.942 & 0.963 & \textbf{1.000} & 0.727 \\
Tokens / scenario           & 1540  & 1110  & 1291  & 0 \\
\bottomrule
\end{tabular}
\end{table}

\noindent The LLM arms \textbf{detect attack events precisely} --- event-level recall $0.64$--$0.73$ at
precision $0.94$--$1.00$, \emph{higher precision than the rules} ($0.73$) --- yet score near-zero at the
technique level. The rules (A4) win technique-level recall ($0.911$) because they encode the exact
sub-technique each scenario uses; the LLM, even given the closed technique vocabulary and parent-technique
credit, rarely names the exact technique. The bottleneck is \textbf{technique attribution, not cross-domain
event detection}.

\subsection{Primary hypotheses}
\textbf{H1 (LLM vs rules, technique-level recall):} the best LLM arm (A1) trails A4 by a mean of $-0.874$
(95\% CI $[-0.959,-0.767]$, Cohen's $d_z=-4.39$, permutation $p<0.001$, Holm-corrected). H1 is
\textbf{not supported} --- and, on the strict technique-level metric, the LLM is significantly \emph{worse}.
\textbf{H2 (multi-agent vs single, F1):} A1 vs A2 differ by $+0.027$ (95\% CI $[-0.004,0.062]$, $d_z=0.42$,
$p=0.19$): we \textbf{fail to reject} H2 --- multi-agent decomposition adds no measurable value, while costing
$\sim$40\% more tokens (1540 vs 1110).

\subsection{Pre-filter cost and latency (C3)}
The deterministic pre-filter keeps $\sim$82\% of events on multi-stage (filtering ratio $0.82$; A3 runs
unfiltered at $1.0$). It reduces LLM token cost (A2 $1110$ vs A3 $1291$, $\approx$14\%) --- but at an
event-recall cost: \emph{A3 (no pre-filter) detects more attack events than A2} ($0.732$ vs $0.641$). Thus the
pre-filter is a genuine cost-vs-recall trade-off, and for a capable reader model it discards real detections.
A4 (rules) and SIGMA incur zero LLM cost. \todo{cost--accuracy frontier figure once all categories are run.}

% =====================================================================
\section{Failure-Mode Analysis}\label{sec:failure}
% Owner: Atishay.
\textbf{Technique attribution is the dominant LLM failure.} Because event-level precision is $\geq 0.94$ while
technique-level recall is $\sim$0.04, almost every event the LLM flags \emph{is} an attack event, but the
attached ATT\&CK id is usually wrong. Before the technique vocabulary was supplied, the model labelled events
with techniques outside the benchmark entirely (e.g., T1569, T1222); constraining the label space fixed the
out-of-vocabulary errors but not the within-vocabulary confusions.

\textbf{Rules (A4) failure.} A4 misses \emph{Cloud Infrastructure Discovery} (T1580) entirely on multi-stage
(its signature cannot distinguish T1580 from the sibling T1526), and over-flags on benign scenarios
(false-positive precision $0.73$) because every \texttt{ListBuckets}/\texttt{GetObject} trips a signature.

\textbf{Pre-filter recall stress.} On multi-stage the pre-filter retains $0.967$ of ground-truth events; the
recall cost concentrates in the low-and-slow category, where sparse, subtle events are most likely to be
dropped before any arm sees them. \todo{report low-and-slow pre-filter recall from the full run.}

% =====================================================================
\section{Discussion}\label{sec:discussion}
% Owner: Anna
Our headline is a \emph{decomposition}: on AWS multi-stage kill chains, a mid-sized open LLM performs
cross-domain attack-event detection competitively and at higher precision than deterministic rules, but fails
at exact ATT\&CK-technique attribution. For a SOC, this suggests LLMs are promising as \emph{high-precision
triage / correlation} aids --- surfacing the events that matter with few false alarms --- while exact technique
labelling is better left to rules or human analysts. Multi-agent decomposition did not pay for its extra cost
(H2), and the pre-filter trades a modest cost saving for lost detections, so a cost-sensitive deployment might
skip it when the model can ingest the full stream.

\textbf{Why the rules win technique-level, and why that is not the whole story.} On this \emph{synthetic}
benchmark the rules are near-optimal \emph{by construction}: their signatures are effectively the inverse of
the scenario generator, so A4's $0.91$/$0.97$ scores are an upper bound a real deployment would not reach. The
strict technique-level metric therefore structurally favours rules that encode the answer key; we accordingly
report event-level detection as the headline and technique-level as a stricter secondary, and defer the
primary-metric decision to the pre-registration sign-off. A real-telemetry run, where no rule is a perfect
inverse, is the decisive next test. \todo{supervisor: ratify primary metric (event- vs technique-level).}

% =====================================================================
\section{Threats to Validity}\label{sec:threats}
% Owner: shared (docs/week1/15)
\emph{External:} synthetic scenarios may not generalise---mitigated by real-incident
grounding and (partial) real-AWS validation. \emph{Authorship bias:} same team authors
scenarios and system---mitigated by a sealed held-out set and inter-rater review.
\emph{Construct:} bespoke metrics may reward conformity---mitigated by leading with
standard metrics. \emph{Internal:} LLM non-determinism---mitigated by a pinned model,
multi-seed runs, and reported variance. \emph{Statistical:} small per-category $n$---the
power analysis restricts confirmatory claims to two primary tests; other categories are
descriptive. \emph{Reproducibility:} model drift/deprecation---mitigated by version
pinning and full artifact release; adversarial LLM evasion is explicitly out of scope.
\emph{Baseline coverage:} GuardDuty requires real-AWS access with a $\geq$7-day warm-up;
it is deferred to a follow-up study. LLMCloudHunter generates detection rules from CTI
reports (a different task) and is therefore positioned in related work rather than scored
on the benchmark; the community Sigma baseline (SIGMA arm) provides an independent
rules-only comparison that does not require a managed AWS service.

% =====================================================================
\section{Conclusion}\label{sec:conclusion}
% Owner: Anna
\result{summary of findings including any negative results; the benchmark as the durable
contribution; future work (real-AWS breadth, external baselines, Zeek network telemetry,
adversarial evasion).}

\section*{Availability}
The generator, manifests, schema, matching function, and analysis scripts are released at
\url{https://github.com/therealannaa/CloudSentinel} \todo{swap to the archival DOI on release}.

\section*{Acknowledgment}
The authors thank Dr.~S.~Nagasundari (ISFCR, PES University) for supervision.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
